---
title: Debug of k2rt 02/03 try
author: "Sylvain Schmitt"
output:
  bookdown::html_document2:
    theme: readable
    toc: true
    toc_float: yes
    number_sections: yes
  bookdown::pdf_document2:
    toc: false
    number_sections: false
---

```{r setup, include=FALSE}
rm(list = ls()) ; invisible(gc()) ; set.seed(42)
library(knitr)
opts_chunk$set(
  echo = T, message = T, warning = T, fig.height = 6, fig.width = 8,
  cache = T, cache.lazy = F)
```

# Files

```{bash}
tree
```

# First example

## Untreated (tsv)

```{bash}
head -n 3 untreated.tsv
```

* Genes: 
    * TRINITY_DN765241_c0_g4_i2
    * TRINITY_DN765241_c0_g4_i1
* SNP: bcc_9953|Cycle_14|Type_0a
* Reason: Bubble as no Kissplice connection

## SNPs (fa)

```{bash}
grep bcc_9953\|Cycle_14\|Type_0a results_coherent_type_0a.fa
```

SNP bcc_9953 is correctly defined one time in the fa file:

* bcc_9953|Cycle_14|Type_0a|upper_path_length_83
* bcc_9953|Cycle_14|Type_0a|lower_path_length_83

## Gene ORF (bed)

```{r}
# grep TRINITY_DN765241_c0_g4_i2 symphonia.trinity500.fasta.transdecoder.bed
# grep TRINITY_DN765241_c0_g4_i1 symphonia.trinity500.fasta.transdecoder.bed
```

* Gene TRINITY_DN765241_c0_g4_i2 is absent in the bed file. No ORF ? Not functional ?
* Gene TRINITY_DN765241_c0_g4_i1 is absent in the bed file. No ORF ? Not functional ?

## SNPs in Genes (psl)

```{bash}
grep bcc_9953\|Cycle_14\|Type_0a all_symphonia_juvs_type0a.psl
```

SNP bcc_9953|Cycle_14|Type_0a is defined in two genes:

* TRINITY_DN765241_c0_g4_i2
* TRINITY_DN765241_c0_g4_i1

## Conclusion

It seems the issue come from the fact that the SNP is defined in two genes (same as with example data).

# Second example

## Untreated (tsv)

```{bash}
grep bcc_97365\|Cycle_0\|Type_0a untreated.tsv
```

* Genes: 
    * TRINITY_DN781930_c2_g3_i3
    * TRINITY_DN781930_c2_g3_i2
* SNP: bcc_97365|Cycle_0|Type_0a
* Reason: Bubble as no Kissplice connection

## SNPs (fa)

```{bash}
grep bcc_97365\|Cycle_0\|Type_0a results_coherent_type_0a.fa
```

SNP bcc_9953 is correctly defined one time in the fa file:

* bcc_97365|Cycle_14|Type_0a|upper_path_length_83
* bcc_97365|Cycle_14|Type_0a|lower_path_length_83

## Gene ORF (bed)

```{bash}
grep TRINITY_DN781930_c2_g3_i3 symphonia.trinity500.fasta.transdecoder.bed
grep TRINITY_DN781930_c2_g3_i2 symphonia.trinity500.fasta.transdecoder.bed
```

* Gene TRINITY_DN781930_c2_g3_i3 has an ORF
* Gene TRINITY_DN781930_c2_g3_i2 has an ORF

## SNPs in Genes (psl)

```{bash}
grep bcc_97365\|Cycle_0\|Type_0a all_symphonia_juvs_type0a.psl
```

SNP bcc_9953|Cycle_14|Type_0a is defined in two genes:

* TRINITY_DN781930_c2_g3_i3
* TRINITY_DN781930_c2_g3_i2

## Conclusion

It seems the issue come from the fact that the SNP is defined in two genes (same as with example data). And this time the two genes have ORFs so the issue is not coming from the bed file.

# Debug test

If we use the second example with SNP bcc_97365|Cycle_0|Type_0a and genes TRINITY_DN781930_c2_g3_i3 & TRINITY_DN781930_c2_g3_i2, but with only gene TRINITY_DN781930_c2_g3_i3 in the psl file.

```{bash}
mkdir debug_test
SNP=bcc_97365\|Cycle_0\|Type_0a
Gene=TRINITY_DN781930_c2_g3_i3
file_fa=results_coherent_type_0a.fa
file_bed=symphonia.trinity500.fasta.transdecoder.bed
file_psl=all_symphonia_juvs_type0a.psl
rm ./debug_test/test.fa ./debug_test/test.bed ./debug_test/test.psl
cp $file_fa ./debug_test/test.fa
grep  $Gene $file_bed >> ./debug_test/test.bed
grep  $SNP $file_psl | grep $Gene >> ./debug_test/test.psl
```

Now we run again k2rt with an output for untreated:

```{bash}
cd debug_test/
rm untreated.tsv mainoutput.tsv
kissplice2reftranscriptome -b test.bed -t test.psl -k test.fa -u untreated.tsv -o mainoutput.tsv
```

Checking for outputs and untreated Bubbles:

```{bash}
cat debug_test/mainOutput1520450514.32.tsv
cat debug_test/untreated.tsv
```

And once again `k2rt` is not able to connect the kissplice fa file with others.

# *Break in code*

We can use `python` code to check line lecture and correspondance between bed and psl files.

## Data gathering

### Code

```{python, eval=F}
ktp.formatKisspliceTable()
ktp.createKisspliceDictionary()
blattp.formatBlatTable()
blattp.createBlatDictionary()
for i in range(0, len(blattp.blatTable)):
  skipRow = False
  qNameTable = blatbd.getQueryNameTable(blattp.blatTable[blatRowNumber])
  snpId = blatbd.getSnpId(blattp.blatTable[blatRowNumber])
  componentId = blattp.blatTable[blatRowNumber][13]
  blatbd.getLowerPath(blattp.blatTable, blatRowNumber, blattp.blatDictionary, snpId)
  
  if blatbd.isRowWithoutKisspliceConnection(ktp.kisspliceDictionary, blattp.blatTable[blatRowNumber]) is True:

    if ap.getUntreatableBubblesOutputFilePath() is not False:
      untreatedReason = "Bubble as no Kissplice connection"
      ofw.writeInUntreatableBubblesTsv(untreatableBubblesOutputFilePath, componentId, snpId, untreatedReason, isSpecificCondition)
    skipRow = True
```


## blat table & dictionnary (psl)

### Code

```{python, eval=F}
class BlatTableParser:

  def formatBlatTable(self):
    self.blatTable = [element.strip('\n').strip(',').split('\t') for element in self.blatTable]

  def createBlatDictionary(self):
    for element in self.blatTable:
      snpDictionaryValue = []
      for i in range(0, len(element)):
        if i == 13: # Gene
          compIdTable = element[i].split("_")
          trunkedCompId = "_".join(compIdTable[0:-1])
          snpDictionaryValue.append(trunkedCompId)
          snpDictionaryValue.append(compIdTable[-1])
        else:
          if i == 9: # SNP
            snpIdTable = element[i].split("|")
            snpKey = snpIdTable[0] + "|" + snpIdTable[1] + "|" + snpIdTable[2]
          snpDictionaryValue.append(element[i])
          
      if snpKey in self.blatDictionary:
        self.blatDictionary[snpKey].append(snpDictionaryValue)
      else:
        self.blatDictionary[snpKey] = [snpDictionaryValue]
```

### Home made

```{python}
element = "82	1	0	0	0	0	0	0	-	bcc_97365|Cycle_0|Type_0a|lower_path_Length_83|C1_0|C2_0|C3_0|C4_0|C5_0|C6_0|C7_0|C8_0|C9_7|C10_1|C11_0|C12_0|C13_0|C14_0|C15_0|C16_0|C17_0|C18_0|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_0|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_0|Q6_0	83	0	83	TRINITY_DN781930_c2_g3_i3	791	389	472	1	83,	0,	389,"
element = element.strip('\n').strip(',').split('\t')
blatTable = element
snpDictionaryValue = []
compIdTable = element[13].split("_")
trunkedCompId = "_".join(compIdTable[0:-1])
snpDictionaryValue.append(trunkedCompId)
snpDictionaryValue.append(compIdTable[-1])
snpIdTable = element[9].split("|")
snpKey = snpIdTable[0] + "|" + snpIdTable[1] + "|" + snpIdTable[2]
snpDictionaryValue.append(element[9])
blatDictionnaryKey = snpKey
blatDictionnaryValue = snpDictionaryValue
print blatTable
print blatDictionnaryKey
print blatDictionnaryValue
```

## kissplice table & dictionnary (fa)

### Code

```{python, eval=F}
import re

class KisspliceTableParser():

  def formatKisspliceTable(self):
    self.kisspliceTable = [element.strip('>').split('\n') for element in self.kisspliceTable]

    temporaryTable = []
    rowNumber = -1
    for element in self.kisspliceTable:
      if re.match("^bcc.*$", element[0]):
        rowNumber += 1
        temporaryTable.append(element)
      else:
        temporaryTable[rowNumber][1] = temporaryTable[rowNumber][1] + element[0]

    self.kisspliceTable = temporaryTable

  def createKisspliceDictionary(self):
    for element in self.kisspliceTable:
      self.kisspliceDictionary[element[0]] = element[1]
```

### Home made

```{python}
element = ">bcc_97365|Cycle_0|Type_0a|lower_path_Length_83|C1_0|C2_0|C3_0|C4_0|C5_0|C6_0|C7_0|C8_0|C9_7|C10_1|C11_0|C12_0|C13_0|C14_0|C15_0|C16_0|C17_0|C18_0|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_0|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_0|Q6_0|Q7_0|Q8_0|Q9_71|Q10_71|Q11_0|Q12_0|Q13_0|Q14_0|Q15_0|Q16_0|Q17_0|Q18_0|Q19_0|Q20_0|Q21_0|Q22_0|Q23_0|Q24_0|Q25_0|Q26_0|Q27_0|Q28_0|Q29_0|Q30_0|Q31_0|Q32_0|Q33_0|Q34_0|Q35_0|Q36_0|Q37_0|Q38_0|Q39_0|Q40_0|Q41_0|Q42_0|Q43_0|Q44_0|Q45_0|Q46_0|Q47_0|Q48_0|Q49_0|Q50_0|Q51_0|Q52_0|Q53_0|Q54_0|Q55_0|Q56_0|Q57_0|Q58_0|Q59_0|Q60_0|Q61_0|Q62_0|Q63_0|Q64_0|Q65_0|Q66_0|Q67_0|Q68_0|Q69_0|Q70_0|Q71_0|Q72_0|Q73_0|Q74_0|rank_1.00000\nAATCTTGCGGAGTATCTTGTCGGGTTGTCCTGTTCTTGAATTGTTGAAGTTGTACAAATGCATTGGGATTAATGAGGTTGATA"
element = element.strip('>').split('\n')
kisspliceTable = [[element[0],element[1]]]
kisspliceKey = element[0]
kisspliceValue = element[1]
print kisspliceTable
print kisspliceKey
print kisspliceValue
```

<!-- ## trintity dictionnary (bed) -->

<!-- ### Code -->

<!-- ```{python, eval=F} -->
<!-- class TrinityBedTableParser(): -->
<!--   def __init__(self): -->
<!--     self.trinityBedTable = [] -->
<!--     self.trinityBedDictionary = {} -->

<!--   def formatTrinityBedTable(self): -->
<!--     self.trinityBedTable = [element.strip('\n').split('\t') -->
<!--                             for element in self.trinityBedTable] -->

<!--   def createTrinityBedDictionary(self): -->
<!--     for element in self.trinityBedTable: -->
<!--       dictionaryValue = [] -->
<!--       for i in range(1, len(element)): -->
<!--         dictionaryValue.append(element[i]) -->
<!--       if self.trinityBedDictionary.get(element[0]) is not None: -->
<!--         rowAlignment = int(self.trinityBedDictionary.get(element[0])[6]) - \ -->
<!--                        int(self.trinityBedDictionary.get(element[0])[5]) -->
<!--         if rowAlignment < (int(dictionaryValue[6]) - int(dictionaryValue[5])): -->
<!--           self.trinityBedDictionary[element[0]] = dictionaryValue -->
<!--       else: -->
<!--         self.trinityBedDictionary[element[0]] = dictionaryValue -->
<!-- ``` -->

<!-- ### Home made -->

<!-- ```{python} -->
<!-- element = "TRINITY_DN781930_c2_g3_i3	0	791	ID=TRINITY_DN781930_c2_g3::TRINITY_DN781930_c2_g3_i3::g.35298::m.35298;TRINITY_DN781930_c2_g3::TRINITY_DN781930_c2_g3_i3::g.35298;ORF_type:5prime_partial_len:260_(-)	0	-	9	789	0	1	791	0" -->
<!-- element = element.strip('\n').split('\t') -->
<!-- # print int(element[6+1])-int(element[5+1]) -->
<!-- print element[0] -->
<!-- print element[1:len(element)] -->
<!-- ``` -->

## blat and kissplice match

### Code

```{python, eval=F}
def isRowWithoutKisspliceConnection(self, kisspliceDictionary, blatRow):
  if blatRow[9] in kisspliceDictionary:
    return False
  else:
    return True
```

### Home made

```{python}
# Blat
element = "82	1	0	0	0	0	0	0	-	bcc_97365|Cycle_0|Type_0a|lower_path_Length_83|C1_0|C2_0|C3_0|C4_0|C5_0|C6_0|C7_0|C8_0|C9_7|C10_1|C11_0|C12_0|C13_0|C14_0|C15_0|C16_0|C17_0|C18_0|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_0|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_0|Q6_0	83	0	83	TRINITY_DN781930_c2_g3_i3	791	389	472	1	83,	0,	389,"
element = element.strip('\n').strip(',').split('\t')
blatTable = element
snpDictionaryValue = []
compIdTable = element[13].split("_")
trunkedCompId = "_".join(compIdTable[0:-1])
snpDictionaryValue.append(trunkedCompId)
snpDictionaryValue.append(compIdTable[-1])
snpIdTable = element[9].split("|")
snpKey = snpIdTable[0] + "|" + snpIdTable[1] + "|" + snpIdTable[2]
snpDictionaryValue.append(element[9])
blatDictionnaryKey = snpKey
blatDictionnaryValue = snpDictionaryValue
# kisspliceDictionnary
element = ">bcc_97365|Cycle_0|Type_0a|lower_path_Length_83|C1_0|C2_0|C3_0|C4_0|C5_0|C6_0|C7_0|C8_0|C9_7|C10_1|C11_0|C12_0|C13_0|C14_0|C15_0|C16_0|C17_0|C18_0|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_0|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_0|Q6_0|Q7_0|Q8_0|Q9_71|Q10_71|Q11_0|Q12_0|Q13_0|Q14_0|Q15_0|Q16_0|Q17_0|Q18_0|Q19_0|Q20_0|Q21_0|Q22_0|Q23_0|Q24_0|Q25_0|Q26_0|Q27_0|Q28_0|Q29_0|Q30_0|Q31_0|Q32_0|Q33_0|Q34_0|Q35_0|Q36_0|Q37_0|Q38_0|Q39_0|Q40_0|Q41_0|Q42_0|Q43_0|Q44_0|Q45_0|Q46_0|Q47_0|Q48_0|Q49_0|Q50_0|Q51_0|Q52_0|Q53_0|Q54_0|Q55_0|Q56_0|Q57_0|Q58_0|Q59_0|Q60_0|Q61_0|Q62_0|Q63_0|Q64_0|Q65_0|Q66_0|Q67_0|Q68_0|Q69_0|Q70_0|Q71_0|Q72_0|Q73_0|Q74_0|rank_1.00000\nAATCTTGCGGAGTATCTTGTCGGGTTGTCCTGTTCTTGAATTGTTGAAGTTGTACAAATGCATTGGGATTAATGAGGTTGATA"
element = element.strip('>').split('\n')
kisspliceTable = [[element[0],element[1]]]
kisspliceKey = element[0]
kisspliceValue = element[1]
# match
print blatTable[9]
print kisspliceKey
```

## Conclusion

There is effectivelly a mismatch between SNP keys `blat` psl file and `kissplice` fa file. It seems that the SNP keys in the `blat` psl file has been shorten (see diff file with `Geany` in `debug_test` folder).

# Debug test 2

If we replace the uncomplete SNP key from the `blat` file with the one from `kissplice`

```{bash}
mkdir debug_test2
SNP=bcc_97365\|Cycle_0\|Type_0a
Gene=TRINITY_DN781930_c2_g3_i3
file_fa=results_coherent_type_0a.fa
file_bed=symphonia.trinity500.fasta.transdecoder.bed
rm ./debug_test2/test2.fa ./debug_test2/test2.bed ./debug_test2/test2.psl
cp $file_fa ./debug_test2/test2.fa
grep  $Gene $file_bed >> ./debug_test2/test2.bed
cp ./new.psl ./debug_test2/test2.psl
```

Now we run again k2rt with an output for untreated:

```{bash}
cd debug_test2/
rm untreated2.tsv mainoutput2.tsv
kissplice2reftranscriptome -b test2.bed -t test2.psl -k test2.fa -u untreated2.tsv -o mainoutput2.tsv
```

Checking for outputs and untreated Bubbles:

```{bash}
cat debug_test2/mainoutput2.tsv
cat debug_test2/untreated2.tsv
```

**And it works !** Consequently we now need to find why `blat` is writting bad SNP key.

# Blat bug investigation

## Blat script:

```{bash, eval=F}
reftranscriptway=$way/$rnalibname/$rnalibname.fasta
kissplice_res=/media/toshiba/AREA/symphonia.trinity500.kissplice/symphonia.results.fullsample.new/
blat_res=/media/toshiba/AREA/symphonia.trinity500.kissplice/blat.symphonia.trinity500.new
/usr/local/bin/blat $reftranscriptway $kissplice_res/*_type_0b.fa $blat_res/all_symphonia_juvs_type0b.psl
```

## Kissplice result old and new:

```{bash, eval=F}
tabebuia-ssh
kissplice_fold=/media/toshiba/AREA/symphonia.trinity500.kissplice
kissplice_res_old=$kissplice_fold/symphonia.results.fullsample
kissplice_res_new=$kissplice_fold/symphonia.results.fullsample.new
head $kissplice_res_old/*type_0a.fa
head $kissplice_res_new/*type_0a.fa
```

```{r, eval=F}
# head $kissplice_res_old/*type_0a.fa
>bcc_126518|Cycle_4744|Type_0a|upper_path_length_83
AAAAAAGCAGTTCCTATCATAACATGTAATCCATGAAAACCTGTTCCAAAATAGAAACATGATGAATATGTTCCATCTGAAAT
```

```{r, eval=F}
# head $kissplice_res_new/*type_0a.fa
>bcc_9953|Cycle_14|Type_0a|upper_path_length_83|C1_0|C2_0|C3_0|C4_0|C5_1|C6_1|C7_1|C8_3|C9_0|C10_3|C11_1|C12_0|C13_1|C14_0|C15_0|C16_0|C17_0|C18_1|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_2|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_73|Q6_71|Q7_73|Q8_73|Q9_0|Q10_73|Q11_71|Q12_0|Q13_73|Q14_0|Q15_0|Q16_0|Q17_0|Q18_73|Q19_0|Q20_0|Q21_0|Q22_0|Q23_0|Q24_0|Q25_0|Q26_73|Q27_0|Q28_0|Q29_0|Q30_0|Q31_0|Q32_0|Q33_0|Q34_0|Q35_0|Q36_0|Q37_0|Q38_0|Q39_0|Q40_0|Q41_0|Q42_0|Q43_0|Q44_0|Q45_0|Q46_0|Q47_0|Q48_0|Q49_0|Q50_0|Q51_0|Q52_0|Q53_0|Q54_0|Q55_0|Q56_0|Q57_0|Q58_0|Q59_0|Q60_0|Q61_0|Q62_0|Q63_0|Q64_0|Q65_0|Q66_0|Q67_0|Q68_0|Q69_0|Q70_0|Q71_0|Q72_0|Q73_0|Q74_0|rank_1.00000
GACAGATCCGACTGACTTATTTGATGATTGATTGGAGAATCGAAGTGGTCTTTGCTTTGGAAAATTCGATTTTATGTTGGATA
```

## Kissplice result old and new:

```{bash, eval=F}
tabebuia-ssh
blat_fold=/media/toshiba/AREA/symphonia.trinity500.kissplice
blat_res_old=$kissplice_fold/blat.symphonia.trinity500
blat_res_new=$kissplice_fold/blat.symphonia.trinity500.new
head $blat_res_old/*type0a.psl
head $blat_res_new/*type0a.psl
```

```{r, eval=F}
# head $blat_res_old/*type0a.psl
75	8	0	0	0	0	0	0	-	bcc_126518|Cycle_4744|Type_0a|upper_path_length_83	83	0	83	TRINITY_DN798856_c11_g2_i1	663	226	309	1	83,	0,	226,
```

```{r, eval=F}
# head $blat_res_new/*type0a.psl
82	1	0	0	0	0	0	0	+	bcc_9953|Cycle_14|Type_0a|upper_path_length_83|C1_0|C2_0|C3_0|C4_0|C5_1|C6_1|C7_1|C8_3|C9_0|C10_3|C11_1|C12_0|C13_1|C14_0|C15_0|C16_0|C17_0|C18_1|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_2|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_73|Q6_	83	0	83	TRINITY_DN765241_c0_g4_i2	765	365	448	1	83,	0,	365,
```

## Conclusion

**It seems `blat` does not accept excessively long SNP key !**

```{r}
SNP_key = "bcc_9953|Cycle_14|Type_0a|upper_path_length_83|C1_0|C2_0|C3_0|C4_0|C5_1|C6_1|C7_1|C8_3|C9_0|C10_3|C11_1|C12_0|C13_1|C14_0|C15_0|C16_0|C17_0|C18_1|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_2|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_73|Q6_71|Q7_73|Q8_73|Q9_0|Q10_73|Q11_71|Q12_0|Q13_73|Q14_0|Q15_0|Q16_0|Q17_0|Q18_73|Q19_0|Q20_0|Q21_0|Q22_0|Q23_0|Q24_0|Q25_0|Q26_73|Q27_0|Q28_0|Q29_0|Q30_0|Q31_0|Q32_0|Q33_0|Q34_0|Q35_0|Q36_0|Q37_0|Q38_0|Q39_0|Q40_0|Q41_0|Q42_0|Q43_0|Q44_0|Q45_0|Q46_0|Q47_0|Q48_0|Q49_0|Q50_0|Q51_0|Q52_0|Q53_0|Q54_0|Q55_0|Q56_0|Q57_0|Q58_0|Q59_0|Q60_0|Q61_0|Q62_0|Q63_0|Q64_0|Q65_0|Q66_0|Q67_0|Q68_0|Q69_0|Q70_0|Q71_0|Q72_0|Q73_0|Q74_0|rank_1.00000"
bad_SNP_key = "bcc_9953|Cycle_14|Type_0a|upper_path_length_83|C1_0|C2_0|C3_0|C4_0|C5_1|C6_1|C7_1|C8_3|C9_0|C10_3|C11_1|C12_0|C13_1|C14_0|C15_0|C16_0|C17_0|C18_1|C19_0|C20_0|C21_0|C22_0|C23_0|C24_0|C25_0|C26_2|C27_0|C28_0|C29_0|C30_0|C31_0|C32_0|C33_0|C34_0|C35_0|C36_0|C37_0|C38_0|C39_0|C40_0|C41_0|C42_0|C43_0|C44_0|C45_0|C46_0|C47_0|C48_0|C49_0|C50_0|C51_0|C52_0|C53_0|C54_0|C55_0|C56_0|C57_0|C58_0|C59_0|C60_0|C61_0|C62_0|C63_0|C64_0|C65_0|C66_0|C67_0|C68_0|C69_0|C70_0|C71_0|C72_0|C73_0|C74_0|Q1_0|Q2_0|Q3_0|Q4_0|Q5_73|Q6_"
length(strsplit(SNP_key, "")[[1]])
length(strsplit(bad_SNP_key, "")[[1]])
```

# Solution ?

1. Search the `blat` issue on the web 
1. Find the origin of the long SNP keys in `kissplice`
1. Code a function to correct the names in the `blat` psl file with those from the `kissplice` fa file
1. _Hack_ `kissplice2reftranscriptome` code to be more permissive (accept the SNP code match only with the first informations, see snpKey in the `createBlatDictionary` function)
